---
title       : Residency permits to Denmark
subtitle    : 2006 - 2015
author      : Claus Gaarde Pedersen
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : solarized_light
widgets     : [bootstrap]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
ext_widgets : {rCharts: [libraries/nvd3]}
---

## Forreign immigration to Denmark
```{r echo=FALSE, message=FALSE}
require(dplyr)
require(rCharts)
```


In this presentation, we will look at how many people immigrate to Denmark.

This will be done by looking at the number of people getting residency permits.

Hopefully this can provide some basic information that will be usefull when trying to digest the medias attention to this subject.


### Included in this presentation is :

1. Overview of the number of residency permits per year by barplot in rCharts

2. Mapped number of residency permits by country through rworldmap in shiny

3. Links to the ressources used.

--- .class #id 

## Number of residency permits by type
```{r echo=FALSE}
resi <- read.csv("tidy_residency.csv", stringsAsFactors=FALSE)
```

```{r}
# Using the same csv as for the shiny part later.
# the data is summed by residency permit type. look at shiny part for country details 
resi <- resi %>% group_by(year, type) %>% summarize(permits=sum(n)) %>%
    select(year, type, permits)
```

```{r results='asis', echo=FALSE, message=FALSE}
n1 <- nPlot(permits ~ year, group = 'type', type='multiBarChart',
            data=as.data.frame(resi))
n1$show('inline', cdn=TRUE)
```

---

## Mapping of residency permits by country

rworldmap picture

link to shiny

---

## Ressources

Data downloaded from statistikbanken.dk

http://www.statistikbanken.dk/statbank5a/default.asp?w=1280

Search for statistic VAN66 english version

The data is downloaded as matrix-csv and processed in R

link to exploratory processing here github link
where the whole source for the slidify and shiny parts also can be found
